A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-07-29 07_Manuscript.Rmd
attempting to implement lua styles

>>>>

---
title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
author:
   - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
   - Emerson Del Ponte:
      institute: UFV
   - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::word_document2:
    toc: no
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      reference_docx: "Manuscript2Word_Template.docx"
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
abstract: |
         Insert abstract here.
---

### 2020-07-29 vignette/Manuscript2Word.Rmd
attempting to implement lua styles

---
title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
---

>>>>

---
title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
author:
   - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
   - Emerson Del Ponte:
      institute: UFV
   - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
      toc: no
      pandoc_args:
         - '--lua-filter=scholarly-metadata.lua'
         - '--lua-filter=author-info-blocks.lua'
         reference_docx: "Manuscript2Word_Template.docx"
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
abstract: |
         Insert abstract here.
---
<!-- Should we use the word "fungicide" in the title so it is more searchable for fungicide management? -->
